Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-20 paper/paper.tex
Fix errors in abstract

\begin{abstract}
Software tickets are of valuable importance to the whole computing science 
field - they guide engineers towards better planning, management 
and tracking of their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality,
valuable ticket. This can lead to multiple issues in a company, such as 
increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets, 
Our results show that the presence and type of attachments,
comments complexity, summary and description complexity, presence of stack traces, presence
of steps to reproduce, grammar correctness scores,
as well as the sentiment analysis scores can significantly influence 
the quality of the ticket. We bring a couple of novel aspects to the research
community including one of the largest dataset statistically analysed in this particular field,
as well as state-of-the-art sentiment and grammar correctness analyses.
\end{abstract}

>>>>

\begin{abstract}
Issue trackins systems have become the defacto standard for tracking work items in 
software projects - they guide engineers towards better planning and 
managing their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality,
valuable ticket. This can lead to multiple issues in a company, such as 
increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets, 
Our results show that the presence and type of attachments,
comments complexity, summary and description complexity, presence of stack traces, presence
of steps to reproduce, grammar correctness scores, as well as sentiment can significantly influence 
the quality of the ticket. We supply one of the largest dataset statistically 
analysed in this particular field, as well as state-of-the-art sentiment and grammar correctness analyses.
\end{abstract}
